---
title: "Advertising Diversification"
author: "Filippo Dall'Olio"
format: 
  html:
    code-fold: false
    code-link: true
    page-layout: full
  pdf: 
    toc: true
    number-sections: true
execute: 
  echo: true
  output: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Set Up

```{r}
#|  output: false
# remotes::install_github("f-dallolio/fdutils")
# install.packages("DiagrammeR")
# remotes::install_github("f-dallolio/diversification")
# remotes::install_github("f-dallolio/loadr")

loadr::loadr(
  rlang,
  tidyverse,
  tsibble,
  broom,
  lubridate,
  ggplot2,
  glue,
  skimr,
  fdutils,
  diversification,
  dm,
  update = FALSE
)
```

# Load Data

```{r}
load("data/dm_mydata.rda")
load("data/dm_divdata.rda")
```

# Panel Selection

## Non Div Variables

```{r}
mydata <- dm_mydata %>% 
  pull_tbl(data_df) %>% 
  select(
    id, t, category,
    adawareness, impression, consideration, intention,
    adspend, catspend, clutter
  )

summary_select <- mydata %>% 
  group_by(id, category) %>% 
  summarise(
    N = n(),
    pct_ad1 = mean(adspend > 0),
    max_cons_ad0 = max(consecutive(adspend == 0)),
    mean_adspend = mean(adspend),
    sd_adspend = sd(adspend)
  ) %>% 
  ungroup() %>% 
  filter(
    N == max(N),
    max_cons_ad0 <= 26
  )

model_data <- mydata %>% 
  filter(id %in% pull(summary_select, id))

```

## Div Variables

```{r}
div_names <- c("dayparts", "genres", "networks")

divdata <- map_dfr(
  .x = div_names, 
  .f = ~ dm_divdata %>% 
    pull_tbl(!!.x) %>% 
    filter(id %in% pull(summary_select, id))
  ) %>% 
  transmute(
    id, 
    t, 
    variable, 
    nfx, 
    cfx,
    dfx = 1 - cfx
  )
```

# Models

## Diversification: One Measure

```{r}

```

### Moderator: Hedonic Value

```{r}
fmls <- c(
  # y[1] ~ 1 + lag(y[1]) ~ 1 + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[1]) ~ 1 +  cx + ax + ax:dx + ax:mx + ax:dx:mx,
  # y[2] ~ 1 + 1lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[2]) ~ 1 + lag(y[1]) + cx + ax + ax:dx + ax: mx + ax:dx:mx,
  # y[3] ~ 1 + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[3]) ~ 1 + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax: mx + ax:dx:mx,
  # y[4] ~ 1 + lag(y[3]) + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx 
  diff(y[4]) ~ 1 + lag(y[3]) + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
)
```

### Moderator: Perceived Risk

```{r}

```

### Moderator: Involvement

```{r}

```

### Moderator: Brand Size

```{r}

```

## Diversification: Dayparts and f(Natworks, Genres)

### Moderator: Hedonic Value

```{r}
fmls <- c(
  # y[1] ~ 1 + lag(y[1]) ~ 1 + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[1]) ~ 1 +  cx + ax + ax:dx + ax:mx + ax:dx:mx,
  # y[2] ~ 1 + 1lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[2]) ~ 1 + lag(y[1]) + cx + ax + ax:dx + ax: mx + ax:dx:mx,
  # y[3] ~ 1 + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
  diff(y[3]) ~ 1 + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax: mx + ax:dx:mx,
  # y[4] ~ 1 + lag(y[3]) + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx 
  diff(y[4]) ~ 1 + lag(y[3]) + lag(y[2]) + lag(y[1]) + cx + ax + ax:dx + ax:mx + ax:dx:mx
)
```

### Moderator: Perceived Risk

```{r}

```

### Moderator: Involvement

```{r}

```

### Moderator: Brand Size

```{r}

```

## Diversification: Dayparts and Genres

```{r}
dayparts_data <- divdata %>% 
  filter(variable == "dayparts") %>% 
  select(-variable) %>% 
  rename_with(~ str_c("dayparts_", .x), .cols = c(nfx, cfx, dfx))

genres_data <- divdata %>% 
  filter(variable == "genres") %>% 
  select(-variable) %>% 
  rename_with(~ str_c("genres_", .x), .cols = c(nfx, cfx, dfx))

tot_data <- model_data %>% 
  inner_join(dayparts_data) %>% 
  inner_join(genres_data) %>% 
  rename(
    y1 = adawareness,
    y2 = impression,
    y3 = consideration,
    y4 = intention,
    cx = clutter,
    cax = catspend,
    ax = adspend
  ) %>% 
  group_by(id) %>% 
  mutate(
    ax = ax / 1000,
    cx = cx / 1000,
  ) %>% 
  mutate(
    across(
      .cols = contains(str_c("y", 1:4)),
      .fns = list("lag" = ~ lag(.x)),
      .names = "{.col}_{.fn}"
    ),
    .before = ax
  ) %>% 
  mutate(
    across(
      .cols = contains(c(str_c("y", 1:4), "ax", "cax", "cx")),
      .fns = list("log" = ~ log1p(.x)),
      .names = "{.fn}_{.col}"
    ),
    .before = ax
  ) %>% 
  select(-y1 : -y4, -y1_lag : -y4_lag)

tot_data

 model_data %>% 
  inner_join(dayparts_data) %>% 
  inner_join(genres_data) 
 
 

```

### Moderator: Hedonic Value

```{r}

```

### Moderator: Perceived Risk

```{r}

```

### Moderator: Involvement

```{r}

```

### Moderator: Brand Size

```{r}

```

## Diversification: Dayparts and Natworks

### Moderator: Hedonic Value

```{r}

```

### Moderator: Perceived Risk

```{r}

```

### Moderator: Involvement

```{r}

```

### Moderator: Brand Size

```{r}

```
