---
title: "Advertising Diversification"
author: "Filippo Dall'Olio"
format: 
  html:
    code-fold: false
    code-link: true
    page-layout: full
  pdf: 
    toc: true
    number-sections: true
execute: 
  echo: true
  output: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Set Up

```{r}
#|  output: false
library(tidyverse)
library(rlang)
library(dm)
library(glue)
remotes::install_github("f-dallolio/diversification")
library(diversification)
```

# Load Data

```{r}
load("~/Documents/R_wd/diversification/data/datalist_all_keys.rda")
load("~/Documents/R_wd/diversification/data/datalist.rda")

y_df <- datalist$dv_df %>% 
  select(id, t, adawareness, impression, consideration, intention)

cx_df <- datalist$ad_df %>% 
  select(id, t, clutter)

ax_df <- datalist$ad_df %>% 
  select(id, t, adspend)

mx1_df <- datalist$brandmod_df %>% 
  select(id, size) %>% 
  mutate(size = (size - median(size)) / IQR(size) )

mx2_df <- datalist$catmod_df %>% 
  select(category, risk, involvement, hedonic) %>% 
  mutate(
    across( 
      c(risk : hedonic),
      ~ (.x - median(.x)) / IQR(.x)
    )
  )
```

# Models

## Diversification: One Measure
### Moderator: Hedonic Value

```{r}

```


### Moderator: Perceived Risk

```{r}

```


### Moderator: Involvement

```{r}

```


### Moderator: Brand Size

```{r}

```


## Diversification: Dayparts and f(Natworks, Genres)
### Moderator: Hedonic Value

```{r}

```


### Moderator: Perceived Risk

```{r}

```


### Moderator: Involvement

```{r}

```

### Moderator: Brand Size

```{r}

```


## Diversification: Dayparts and Genres
### Moderator: Hedonic Value

```{r}

```


### Moderator: Perceived Risk

```{r}

```


### Moderator: Involvement

```{r}

```


### Moderator: Brand Size

```{r}

```


## Diversification: Dayparts and Natworks
### Moderator: Hedonic Value

```{r}

```


### Moderator: Perceived Risk

```{r}

```

### Moderator: Involvement
```{r}

```

### Moderator: Brand Size

```{r}

```

